---
title: 'Peer-graded Assignment: Regression Models Course Project'
author: "Daniel Jungen"
date: "29 Dezember 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Manual vs. automatic transmission

"Is an automatic or manual transmission better for MPG?"

And if so:

"Quantify the MPG difference between automatic and manual transmissions"


```{r}
cars<-mtcars
```

In order to get an idea of the distribution of the mpg with respect to the transmission we should take a look at some histograms and boxplots (the horizontal line in the boxplots represents the mean of the mpg in that segment):

```{r echo = FALSE}
cars_am<-cars[cars[,9]==0,]
cars_ma<-cars[cars[,9]==1,]

par(mfrow=c(1,3))

hist(cars$mpg,breaks=10, main="Miles per Gallon", xlab = "Mpg") #all cars
hist(cars_am$mpg, breaks=10, main="Mpg - automatic transmission", xlab = "Mpg") #only automatic transmission
hist(cars_ma$mpg, breaks=10, main="Mpg - manual transmission", xlab = "Mpg") #only manual transmission

par(mfrow=c(1,3))
boxplot(cars$mpg, main = "Boxplot of Mpg")
abline(h=mean(cars$mpg))
boxplot(cars_am$mpg, main = "Mpg - automatic")
abline(h=mean(cars_am$mpg))
boxplot(cars_ma$mpg, main = "Mpg - manual")
abline(h=mean(cars_ma$mpg))
```

Our obervertions imply that there might be a significant difference in mpg per transmission. The figures show the same:
```{r}
mean(cars$mpg)
mean(cars_am$mpg)
mean(cars_ma$mpg)
```

